---
title: "Subnasal Lip Lift: A RealSelf Social Media nalysis"
author: "Monique Arnold"
date: "Accepted for publication by the American Journal of Cosmetic Surgery (AJCS) September 2021."
output:
  html_document: 
    theme: flatly
    highlight: default
    toc: yes
    toc_float: true
    collapsed: false
    smooth_scroll: false
    number_sections: false
---

## Overview

Monique Arnold, BS[1], Sanjeevani Tomar, MD[2], Adam Honeybrook, MBBS[2]  
* Arnold and Tomar contributed equally to this work and are considered to be co-first authors.  
1 University of Pennsylvania, Perelman School of Medicine, Philadelphia, Pennsylvania  
2 Otolaryngology Head and Neck Surgery, Louisiana State University Health Sciences Center, Louisiana   

## Abstract 
**Background:** Social media is a mainstream method for patient reporting of satisfaction with cosmetic procedures, but few studies have reported on this for subnasal lip lifts.  
**Methods:** We performed a social media analysis to identify patient satisfaction with subnasal lip lifts using 578 consecutive reviews on the RealSelf website from lip lift surgery patients between January 2010 and June 2019. Reasons for choosing a surgeon and liking the surgical outcome, surgical and demographic variables, cost, and overall “worth it” scores were recorded, and data analyses were conducted.  
**Results:** Most reviewers were female (526, 97.2%). Predominant reasons for choosing surgeons related to favorable surgeon personality (214, 37.0%) and skillset/artistry (125, 21.6%), and positive rapport established during consultation (88, 15.2%). The aggregate “Worth It Rating” of lip lift surgery using RealSelf’s methodology was 91.6%. The main reasons for liking surgical outcome were that they looked younger, more feminine and “balanced” (97, 16.8%), they liked the new shape and fullness of their lips (58, 10.0%), and they liked that their teeth showed when smiling (30, 5.2%).  
**Conclusions and Relevance:** Overall satisfaction with lip lift surgery is high. Many patients chose their surgeon based on favorable personality traits, emotional connections, and surgeon skillset.  


```{r setup, include=FALSE}
require(knitr)
knitr::opts_chunk$set(echo = TRUE)
mydirectory<-"/Users/moniquearnold/Documents/GitHub/Research-Projects/SubnasalLipliftAnalysis/"
knitr::opts_knit$set(root.dir = mydirectory)

#Clear existing data and graphics
rm(list=ls())
graphics.off()
#Load Hmisc library
library(Hmisc)

# Load  library
pacman::p_load(readxl, plyr, dplyr, MatchIt, mice, knitr, Matching, magrittr, tableone, reshape, reshape2, kableExtra, broom, stringr, rgenoud, tidyverse, Hmisc, uwIntroStats, ggpubr, epitools, survey, lubridate, HardyWeinberg, table1, eeptools,stargazer,compareDF,BiocManager,janitor)

# Print with n digits of precision
fixed_digits <- function(xs, n = 2) {
  formatC(xs, digits = n, format = "f")
}

# Print three digits of a p-value, but use
# the "< .001" notation on tiny values.
format_pval <- function(ps, html = FALSE) {
  tiny <- ifelse(html, "&lt;&nbsp;.001", "< .001")
  ps_chr <- ps %>% fixed_digits(3)
  ps_chr[ps < 0.001] <- tiny
  ps_chr
}

fix_names <- . %>%
  str_replace(".Intercept.", "Intercept")
  
two_digits <- . %>% fixed_digits(2)

table_names <- c("Compound", "Estimate", "SE",
                 "t", "p")

format_model_table <- . %>%
  mutate_each(funs(two_digits),
              -term, -p.value) %>%
  mutate(term = fix_names(term),
         p.value = format_pval(p.value)) %>%
  set_colnames(table_names)

```

```{r inputs, include=FALSE, echo=FALSE}
data <-  read_excel("/Users/moniquearnold/Documents/GitHub/Research-Projects/SubnasalLipliftAnalysis/Data.xlsx", sheet="Sheet1", range="A1:BB579", col_names=TRUE)
location <-  read_excel("/Users/moniquearnold/Documents/GitHub/Research-Projects/SubnasalLipliftAnalysis/Locations.xlsx", sheet="Locations", col_names=TRUE)

#Renaming
names(data)

names(data)[names(data) == "Username"] <- "accountid"
names(data)[names(data) == "Date posted"] <- "date"
names(data)[names(data) == "Age"] <- "age"
names(data)[names(data) == "Sex"] <- "sex"
names(data)[names(data) == "Location"] <- "location"
names(data)[names(data) == "Research length"] <- "research_length"
names(data)[names(data) == "Price"] <- "price"

names(data)[names(data) == "Reason for surgery"] <- "reason_surgery"
names(data)[names(data) == "0 - No response"] <- "reason_surgery_0"
names(data)[names(data) == "1 - long philtrum"] <- "reason_surgery_1"
names(data)[names(data) == "2 - desires tooth show"] <- "reason_surgery_2"
names(data)[names(data) == "3 - unhappy filler"] <- "reason_surgery_3"
names(data)[names(data) == "4 - want look young"] <- "reason_surgery_4"
names(data)[names(data) == "5 - better lip projection"] <- "reason_surgery_5"
names(data)[names(data) == "6 - long/thin lip"] <- "reason_surgery_6"
names(data)[names(data) == "7 - face disproportionate"] <- "reason_surgery_7"
names(data)[names(data) == "8 - dreaded duck"] <- "reason_surgery_8"
names(data)[names(data) == "9 - look sad"] <- "reason_surgery_9"
names(data)[names(data) == "10- revision surgery/ scar management"] <- "reason_surgery_10"
names(data)[names(data) == "11-perfect smile"] <- "reason_surgery_11"

names(data)[names(data) == "Reason liking surgery"] <- "reason_like_lift"
names(data)[names(data) == "0 - no response"] <- "reason_like_lift_0"
names(data)[names(data) == "1 - tooth show"] <- "reason_like_lift_1"
names(data)[names(data) == "2 - look younger/feminine"] <- "reason_like_lift_2"
names(data)[names(data) == "3 - fuller lips/better shape"] <- "reason_like_lift_3"
names(data)[names(data) == "4 - shorter philtrum"] <- "reason_like_lift_4"
names(data)[names(data) == "5 - no scar"] <- "reason_like_lift_5"
names(data)[names(data) == "6 - lip upturned" ] <- "reason_like_lift_6"
names(data)[names(data) == "7 - eyes look bigger" ] <- "reason_like_lift_7"

names(data)[names(data) == "Reason for choosing surgeon"] <- "reason_choose"
names(data)[names(data) == "0 none"] <- "reason_choose_0"
names(data)[names(data) == "1 - reviews"] <- "reason_choose_1"
names(data)[names(data) == "2 - photos"] <- "reason_choose_2"
names(data)[names(data) == "3 - + demeanor"] <- "reason_choose_3"
names(data)[names(data) == "4 - + skillset"] <- "reason_choose_4"
names(data)[names(data) == "5 - training"   ] <- "reason_choose_5"
names(data)[names(data) == "6 - prior exp"] <- "reason_choose_6"
names(data)[names(data) == "7 - fam/fr referral"] <- "reason_choose_7"
names(data)[names(data) == "8 - Doc referral"] <- "reason_choose_8"
names(data)[names(data) == "9 - + emotional"] <- "reason_choose_9"
names(data)[names(data) == "10 - answered Q"] <- "reason_choose_10"
names(data)[names(data) == "11 - price" ] <- "reason_choose_11"
names(data)[names(data) == "12 - technique"] <- "reason_choose_12"
names(data)[names(data) == "13 - other"] <- "reason_choose_13"
names(data)[names(data) == "14 - dr appearance"] <- "reason_choose_14"
names(data)[names(data) == "15 - regrets choosing"] <- "reason_choose_15"

names(data)[names(data) == "Recovery time (days)"] <- "recov_time"
names(data)[names(data) == "Pain"] <- "pain"
names(data)[names(data) == "Anaesthetic"] <- "anaesthetic"
names(data)[names(data) == "Scar?"] <- "scar"
names(data)[names(data) == "Swelling"] <- "swelling"
names(data)[names(data) == "Worth it?"] <- "worth_it"
names(data)[names(data) == "med take"] <- "meds"
names(data)[names(data) == "Others"] <- "other_notes"

```

```{r analysis, include=FALSE, echo=FALSE}
#Cleaning
clean_data <- data
clean_data$date <- as.Date(as.numeric(data$date), origin = "1899-12-30")
clean_data$price<-as.numeric(clean_data$price)

#Age
factor(clean_data$age)
clean_data$age <- as.factor(clean_data$age)
clean_data$age <- factor(clean_data$age, levels=1:5, labels=c("<50","50-59","60-69","70-79","Not reported"))
factor(clean_data$age)
summary_age <- data.frame(table(clean_data$age))
colnames(summary_age) <- c('Age','Frequency')
summary_age$Perc <- summary_age$Frequency / sum(summary_age$Frequency) * 100
summary_age<-rbind(summary_age,summarise_all(summary_age, funs(if(is.numeric(.)) sum(.) else "Total")))

#Sex
factor(clean_data$age)
clean_data$sex <- as.factor(clean_data$sex)
clean_data$sex <- factor(clean_data$sex, levels=1:2, labels=c("Female","Male"))
factor(clean_data$sex)
summary_sex <- data.frame(table(clean_data$sex))
colnames(summary_sex) <- c('Sex','Frequency')
summary_sex$Perc <- summary_sex$Frequency / sum(summary_sex$Frequency) * 100
summary_sex<-rbind(summary_sex,summarise_all(summary_sex, funs(if(is.numeric(.)) sum(.) else "Total")))

#Location
clean_data <- merge(clean_data, location, by=c("location"), all=TRUE)
summary_location <- data.frame(table(clean_data$location_name))
colnames(summary_location) <- c('Location','Frequency')
summary_location$Perc <- summary_location$Frequency / sum(summary_location$Frequency) * 100
summary_location <- summary_location[order(-summary_location$Perc),]
summary_location<-rbind(summary_location,summarise_all(summary_location, funs(if(is.numeric(.)) sum(.) else "Total")))


#Research Length - dropping those that don't fit into 1-6 for now
factor(clean_data$research_length)
clean_data$research_length <- as.factor(clean_data$research_length)
selected<-c(0:6)
clean_data_research <- clean_data[clean_data$research_length %in% selected,]
clean_data_research$research_length <- factor(clean_data_research$research_length, levels=0:6, labels=c("Weeks-Months","Extensive or 1 year+","2 years","3-5 years","5+years","Multiple consultations","Not reported"))
summary_research<- data.frame(table(clean_data_research$research_length))
colnames(summary_research) <- c('Research Length','Frequency')
summary_research$Perc <- summary_research$Frequency / sum(summary_research$Frequency) * 100
summary_research <- summary_research[order(-summary_research$Perc),]
summary_research<-rbind(summary_research,summarise_all(summary_research, funs(if(is.numeric(.)) sum(.) else "Total")))

#Worth it and Price
factor(clean_data$worth_it)
clean_data$worth_it <- as.factor(clean_data$worth_it)
clean_data$worth_it <- factor(clean_data$worth_it, levels=0:3, labels=c("No Response","Yes","No","Not Sure"))
factor(clean_data$worth_it)
summary_worthit <- data.frame(table(clean_data$worth_it))
colnames(summary_worthit) <- c('Worth It','Frequency')
summary_worthit$Perc <- summary_worthit$Frequency / sum(summary_worthit$Frequency) * 100
summary_worthit<-rbind(summary_worthit,summarise_all(summary_worthit, funs(if(is.numeric(.)) sum(.) else "Total")))

price_worthit<-clean_data %>% 
    group_by(worth_it) %>% 
    group_by(worth_it) %>%
    summarize_at(vars(price),funs(count_nomiss=sum(!is.na(.)), mean(., na.rm=TRUE),sd(., na.rm=TRUE)))

summary_worthit_price <- merge(summary_worthit, price_worthit, by.x=c("Worth It"), by.y=c("worth_it"), all=TRUE) 

summary_worthit_price<- summary_worthit_price[complete.cases(summary_worthit_price[ , 1]),] 

clean_data_worthit<- clean_data %>%
  filter(worth_it=="Yes" | worth_it=="No")

#T tests and Fischer Tests for Worth It Scores
ttest1 <- t.test(price ~ worth_it , data = clean_data_worthit, alternative = "two.sided")
fischer_data <- subset(clean_data_worthit,  select=c("worth_it","location_name","research_length","pain","anaesthetic","recov_time")) %>%
  group_by(worth_it) %>%  
  group_by(worth_it)

#Average Price -- #COUNT WHERE NOT MISSING
summary_avgprice<-clean_data %>% 
    mutate(Count = sum(!is.na(price))) %>%
    group_by(Count) %>%
    summarize_at(vars(price), funs(mean(., na.rm=TRUE),sd(., na.rm=TRUE)))

#Investigating price outliers
price_w_outliers<-clean_data %>% 
    summarize_at(vars(price), funs(mean(., na.rm=TRUE),
                                   sd(., na.rm=TRUE), 
                                   max(., na.rm=TRUE),
                                   median(., na.rm=TRUE)))


#For a given continuous variable, outliers are those observations that lie outside 1.5 * IQR, where IQR, the ‘Inter Quartile Range’ is the difference between 75th and 25th quartiles. Look at the points outside the whiskers in below box plot.
v_outliers<-boxplot.stats(clean_data$price)$out
outliers<-data.frame(price=boxplot.stats(clean_data$price)$out) 
outliers<-data.frame(price=outliers[order(outliers$price),])
test_nooutliers<- clean_data[-which(clean_data$price %in% v_outliers),]

price_no_outliers<-test_nooutliers %>% 
    summarize_at(vars(price), funs(mean(., na.rm=TRUE),
                                   sd(., na.rm=TRUE), 
                                   max(., na.rm=TRUE),
                                   median(., na.rm=TRUE)))



plot<-ggplot(clean_data) +
  aes(x = "", y = price) +
  geom_boxplot(fill = "#0c4c8a") +
  theme_minimal()

#Other Notes
other_notes <- data.frame(unique(clean_data$other_notes))
colnames(other_notes) <- c('Other Notes')

#Reasons for Surgery
names(clean_data)
vars_surgery <- grep("reason_surgery_", names(clean_data), value=TRUE) 
summary_surgery<-clean_data %>% summarise_at(vars_surgery,sum, na.rm=TRUE)
summary_surgery <- gather(summary_surgery,factor_key=TRUE)

summary_surgery$Reason[summary_surgery$key == "reason_surgery_0"] <- "Not Reported"
summary_surgery$Reason[summary_surgery$key == "reason_surgery_1"] <- "Long philtrum"
summary_surgery$Reason[summary_surgery$key == "reason_surgery_2"] <- "Want more tooth show when smiling"
summary_surgery$Reason[summary_surgery$key == "reason_surgery_3"] <- "Unsatisfied result with fillers/implants"
summary_surgery$Reason[summary_surgery$key == "reason_surgery_4"] <- "Want to look young"
summary_surgery$Reason[summary_surgery$key == "reason_surgery_5"] <- "Better “up-turn” or projection in the lip corners"
summary_surgery$Reason[summary_surgery$key == "reason_surgery_6"] <- "Long/thin upper lip"
summary_surgery$Reason[summary_surgery$key == "reason_surgery_7"] <- "More proportion and balance for lower face"
summary_surgery$Reason[summary_surgery$key == "reason_surgery_8"] <- "Dreaded duck lips"
summary_surgery$Reason[summary_surgery$key == "reason_surgery_9"] <- "Makes the patient look sad"
summary_surgery$Reason[summary_surgery$key == "reason_surgery_10"] <- "Revision surgery/scar management"
summary_surgery$Reason[summary_surgery$key == "reason_surgery_11"] <- "Perfect smile"

summary_surgery$Perc <- summary_surgery$value / sum(summary_surgery$value) * 100
colnames(summary_surgery) <- c('Variable','Frequency','Reason for Surgery','Percentage')
summary_surgery <- summary_surgery[order(-summary_surgery$Percentage),]
summary_surgery<-rbind(summary_surgery,summarise_all(summary_surgery, funs(if(is.numeric(.)) sum(.) else "Total")))

#Reasons for Liking Surgery
vars_like <- grep("reason_like_lift_", names(clean_data), value=TRUE) 
summary_like<-clean_data %>% summarise_at(vars_like,sum, na.rm=TRUE)
summary_like <- gather(summary_like,factor_key=TRUE)

summary_like$Reason[summary_like$key == "reason_like_lift_0"] <- "Not Reported"
summary_like$Reason[summary_like$key == "reason_like_lift_1"] <- "Tooth show when smiling"
summary_like$Reason[summary_like$key == "reason_like_lift_2"] <- "Look younger/more feminine/face is more balanced"
summary_like$Reason[summary_like$key == "reason_like_lift_3"] <- "Have fuller lips/love the shape of lip"
summary_like$Reason[summary_like$key == "reason_like_lift_4"] <- "Shorter philtrum"
summary_like$Reason[summary_like$key == "reason_like_lift_5"] <- "No scar"
summary_like$Reason[summary_like$key == "reason_like_lift_6"] <- "Lip turns up"
summary_like$Reason[summary_like$key == "reason_like_lift_7"] <- "Eyes look bigger"

summary_like$Perc <- summary_like$value / sum(summary_like$value) * 100
colnames(summary_like) <- c('Variable','Frequency','Reason for Liking Surgery','Percentage')
summary_like <- summary_like[order(-summary_like$Percentage),]
summary_like<-rbind(summary_like,summarise_all(summary_like, funs(if(is.numeric(.)) sum(.) else "Total")))

#Reasons for Choosing Surgeon
vars_choose <- grep("reason_choose_", names(clean_data), value=TRUE) 
summary_choose<-clean_data %>% summarise_at(vars_choose,sum, na.rm=TRUE)
summary_choose <- gather(summary_choose,factor_key=TRUE)

summary_choose$Reason[summary_choose$key == "reason_choose_0"] <- "No reason given"
summary_choose$Reason[summary_choose$key == "reason_choose_1"] <- "Reviews"
summary_choose$Reason[summary_choose$key == "reason_choose_2"] <- "Before/after photos or before/after people"
summary_choose$Reason[summary_choose$key == "reason_choose_3"] <- "Something positive related to personality/demeanor"
summary_choose$Reason[summary_choose$key == "reason_choose_4"] <- "Something positive related to skillset/artistry as a surgeon"
summary_choose$Reason[summary_choose$key == "reason_choose_5"] <- "Training/credentials/expertise"
summary_choose$Reason[summary_choose$key == "reason_choose_6"] <- "Prior personal experience or procedure with doc"
summary_choose$Reason[summary_choose$key == "reason_choose_7"] <- "Referred by friend/family"
summary_choose$Reason[summary_choose$key == "reason_choose_8"] <- "Referred by another medical/healthcare professional"
summary_choose$Reason[summary_choose$key == "reason_choose_9"] <- "Patient had positive emotional response"
summary_choose$Reason[summary_choose$key == "reason_choose_10"] <- "Consultation went well - answered questions/explained"
summary_choose$Reason[summary_choose$key == "reason_choose_11"] <- "Pice"
summary_choose$Reason[summary_choose$key == "reason_choose_12"] <- "Procedure recommendations/technique"
summary_choose$Reason[summary_choose$key == "reason_choose_13"] <- "Other"
summary_choose$Reason[summary_choose$key == "reason_choose_14"] <- "Comment on doc's appearance"
summary_choose$Reason[summary_choose$key == "reason_choose_15"] <- "Regrets choosing surgeon"

summary_choose$Perc <- summary_choose$value / sum(summary_choose$value) * 100
colnames(summary_choose) <- c('Variable','Frequency','Reason for Choosing Surgeon','Percentage')
summary_choose <- summary_choose[order(-summary_choose$Percentage),]
summary_choose<-rbind(summary_choose,summarise_all(summary_choose, funs(if(is.numeric(.)) sum(.) else "Total")))

#Recovery Length
factor(clean_data$recov_time)
clean_data$recov_time <- as.factor(clean_data$recov_time)
summary_recov<-data.frame(table(clean_data$recov_time))
summary_recov$Perc <- summary_recov$Freq / sum(summary_recov$Freq) * 100
summary_recov$Reason[summary_recov$Var1 == 0] <- "No Response"
summary_recov$Reason[summary_recov$Var1 == 1] <- "1-7 days"
summary_recov$Reason[summary_recov$Var1 == 2] <- "8-14 days"
summary_recov$Reason[summary_recov$Var1 == 3] <- "15-30 days"
summary_recov$Reason[summary_recov$Var1 == 4] <- ">30 days"
colnames(summary_recov) <- c('Variable','Frequency','Percentage','Recovery Length')
summary_recov<-rbind(summary_recov,summarise_all(summary_recov, funs(if(is.numeric(.)) sum(.) else "Total")))

#Anasthesia
factor(clean_data$anaesthetic)
clean_data$anaesthetic <- as.factor(clean_data$anaesthetic)
summary_anaesthetic<-data.frame(table(clean_data$anaesthetic))
summary_anaesthetic$Perc <- summary_anaesthetic$Freq / sum(summary_anaesthetic$Freq) * 100
summary_anaesthetic$Reason[summary_anaesthetic$Var1 == 0] <- "No Response"
summary_anaesthetic$Reason[summary_anaesthetic$Var1 == 1] <- "Twilight/Local"
summary_anaesthetic$Reason[summary_anaesthetic$Var1 == 2] <- "Mac"
summary_anaesthetic$Reason[summary_anaesthetic$Var1 == 3] <- "General"
colnames(summary_anaesthetic) <- c('Variable','Frequency','Percentage','Anaesthesia')
summary_anaesthetic<-rbind(summary_anaesthetic,summarise_all(summary_anaesthetic, funs(if(is.numeric(.)) sum(.) else "Total")))

#Post Op Pain
clean_data2 <- clean_data
factor(clean_data2$pain)
clean_data2$pain[clean_data2$pain == "yes" | clean_data$pain == "Yes" ] <- "Yes"
clean_data2$pain <- as.factor(clean_data2$pain)
summary_pain<-data.frame(table(clean_data2$pain))
summary_pain$Perc <- summary_pain$Freq / sum(summary_pain$Freq) * 100
summary_pain$Reason[summary_pain$Var1 == 0] <- "No Response"
summary_pain$Reason[summary_pain$Var1 == 1] <- "None"
summary_pain$Reason[summary_pain$Var1 == 2] <- "Minimal"
summary_pain$Reason[summary_pain$Var1 == 3] <- "Some/Moderate"
summary_pain$Reason[summary_pain$Var1 == 4] <- "Lots"
colnames(summary_pain) <- c('Variable','Frequency','Percentage','Pain')
summary_pain<-rbind(summary_pain,summarise_all(summary_pain, funs(if(is.numeric(.)) sum(.) else "Total")))

```

## Results

### Demographic Characteristics of Subjects
```{r, echo=FALSE}

summary_age %>%
  kable(caption="Table 1. Age Breakdown",digits=1,row.names = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed","striped"), full_width = F, fixed_thead = T)

summary_sex %>%
  kable(caption="Table 2. Sex Breakdown",digits=1,row.names = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed","striped"), full_width = F, fixed_thead = T)
```

### Surgery Specifics
```{r, echo=FALSE} 
summary_location %>% dplyr::select(Location,Frequency,Perc) %>%
  kable(caption="Table 3. Location of Surgery", digits=1,row.names = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed","striped"), full_width = F, fixed_thead = T)

summary_research %>%
  kable(caption="Table 4. Length of  Time of Research of Respondent", digits=1,row.names = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed","striped"), full_width = F, fixed_thead = T)

summary_worthit_price %>%
  kable(caption="Table 5. Worth It Scores and Price Breakdown", digits=2,row.names = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed","striped"), full_width = F, fixed_thead = T)

summary_avgprice %>%
  kable(caption="Table 5. Average Price of Procedure", digits=2,row.names = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed","striped"), full_width = F, fixed_thead = T)

summary_anaesthetic %>% dplyr::select(c(-Variable)) %>%
  kable(caption="Table 6. Anaesthetic Used During Procedure", digits=1,row.names = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed","striped"), full_width = F, fixed_thead = T)

summary_recov %>% dplyr::select(c(-Variable)) %>%
  kable(caption="Table 7. Respondents' Post-Procedural Recovery Time", digits=1,row.names = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed","striped"), full_width = F, fixed_thead = T)

summary_pain %>% dplyr::select(c(-Variable)) %>%
  kable(caption="Table 8. Respondents' Post-Procedural Pain", digits=1,row.names = F) %>% 
  kable_styling(bootstrap_options = c("hover", "condensed","striped"), full_width = F, fixed_thead = T)
```

### Psychosocial Factors Around Surgery
```{r, echo=FALSE}
summary_surgery %>% dplyr::select(c(-Variable)) %>%
  kable(caption="Table 9. Reasons for Surgery",digits=1, row.names = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed","striped"), full_width = F, fixed_thead = T)

summary_choose %>% dplyr::select(c(-Variable)) %>%
  kable(caption="Table 10. Reasons for Choosing Surgeon",digits=1,row.names = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed","striped"), full_width = F, fixed_thead = T)

summary_like %>% dplyr::select(c(-Variable)) %>%
  kable(caption="Table 11. Reasons for Liking Surgery",digits=1, row.names = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed","striped"), full_width = F, fixed_thead = T)
```

### Other Notes from Data
```{r, echo=FALSE}
other_notes %>%
  kable(caption="Table 12. Other Notes") %>%
  kable_styling(bootstrap_options = c("hover", "condensed","striped"), full_width = F, fixed_thead = T)
```

